Viscous Erosion in Porous Media

### 2018-01-09 docs/methods/erosion_methods.tex
modified area_drag.pdf

\begin{keyword}
  Stokes flow \sep Erosion \sep Boundary integral method \sep Shear
  stress \sep \thL~formulation
\end{keyword}

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
%\label{aaa}
\begin{tabular}{c c c}
\hline
\hspace{0.5pc} smoothing parameters, $\eps, \sigma$
\hspace{0.5pc} & final aspect ratio 
\hspace{0.5pc} & final opening angle \\
\hline
20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%

%\begin{comment}
% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
%\label{aaa}
\begin{tabular}{l | c c c c}
\hline
{} & $\eps, \sigma = 20/1024$ & $\eps, \sigma = 10/1024$ & $\eps, \sigma = 5/1024$ & theoretical \\
\hline
final aspect ratio & 2.55 & 2.62 & 2.65 & -- \\
final opening angle & $110^\circ \pm 6^\circ$ & $104^\circ \pm 4^\circ$ & $102^\circ \pm 2^\circ$ & $102^\circ$
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
%\end{comment}

>>>>

\begin{keyword}
  Stokes flow \sep Erosion \sep Boundary integral method \sep Shear
  stress \sep {\thL} formulation
\end{keyword}

@@

% Table
%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{table}%[htbp]
\begin{center}
\caption{Final aspect ratio and opening angle
} 
\vspace{0.3 pc}
%\label{aaa}
\begin{tabular}{c c c}
\hline
\hspace{0.5pc} smoothing parameters: $\eps$ and $\sigma$
\hspace{0.5pc} & final aspect ratio 
\hspace{0.5pc} & final opening angle \\
\hline
20/1024		& 2.55	& $110^\circ \pm 6^\circ$	\\
10/1024		& 2.62	& $104^\circ \pm 4^\circ$	\\
5/1024		& 2.65	& $102^\circ \pm 2^\circ$	\\
\hline
\end{tabular}
\end{center}
\end{table}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% npts = 1024
